Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-02-02 paper/aldebaran.tex

In this paper, we present a re-analysis of these original RV data in which we not only confirm the planetary signal, but detect acoustic oscillations in Aldebaran for the first time. \citet{hatzes1993} noted night-to-night RV variability: in this planet-hunting noise we find an asteroseismic signal. We validate this method and its result with new independent RV observations with the Hertzsprung SONG~Telescope, and photometry from the \ktwo Mission. By measuring the frequency of maximum power of these \emph{p}-mode oscillations, \numax, we can determine the mass of Aldebaran to be $1.16 \pm 0.07$~\msun. This precise stellar mass allows us to calculate that Aldebaran~b and any satellites it may have, although they are now likely to be very hot, would have had equilibrium temperatures comparable to that of the Earth when Aldebaran was on the main sequence. It is possible that they may have once been habitable, billions of years ago.

>>>>

In this paper, we present a re-analysis of these original RV data in which we not only confirm the planetary signal, but detect acoustic oscillations in Aldebaran for the first time. \citet{hatzes1993} noted night-to-night RV variability: this is the noise floor limiting the sensitivity to sub-$M_J$ planets around giants in RV surveys \citep{2005PASJ...57...97S,2014A&A...566A.113J}. We pull out the asteroseismic signal in this planet hunting noise. We validate this method and its result with new independent RV observations with the Hertzsprung SONG~Telescope, and photometry from the \ktwo Mission. By measuring the frequency of maximum power of these \emph{p}-mode oscillations, \numax, we asteroseismically determine the mass of Aldebaran to be $1.16 \pm 0.07$~\msun. This precise stellar mass allows us to calculate that Aldebaran~b and any satellites it may have, although they are now likely to be very hot, would have had equilibrium temperatures comparable to that of the Earth when Aldebaran was on the main sequence. It is possible that they may have once been habitable, billions of years ago.
